\documentclass[10pt,letterpaper]{article}

\usepackage[top=0.5in, bottom=0.5in, left=0.6in, right=0.6in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage[hidelinks]{hyperref}
\usepackage{parskip}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{microtype}

\pagenumbering{gobble}
\setlength{\parindent}{0pt}
\setlist[itemize]{leftmargin=*,itemsep=1pt,topsep=2pt,parsep=0pt}

\titleformat{\section}{\large\bfseries\uppercase}{}{0pt}{}[\vspace{-6pt}\hrulefill\vspace{2pt}]
\titlespacing{\section}{0pt}{8pt}{4pt}

\begin{document}

\begin{center}
{\LARGE \textbf{Islam Abd-Elhady}}\\[4pt]
AI/ML Engineer $|$ LLM Engineer $|$ MLOps Engineer\\[2pt]
Cairo, Egypt $|$ \href{mailto:eslamabdo71239@gmail.com}{eslamabdo71239@gmail.com} $|$ +20 1066463355\\
\href{https://linkedin.com/in/islam-abd-elhady-323523211}{LinkedIn} $|$ \href{https://github.com/Islam-hady9}{GitHub}
\end{center}

\section{Professional Summary}
AI and Machine Learning Engineer with over two years of experience building production-grade large language model systems, retrieval augmented generation pipelines, and multi-agent architectures serving thousands of concurrent users. Specialize in LLMOps, MLOps, GPU optimization, and scalable microservices on AWS, Azure, and Kubernetes. Delivered platforms that reduced design cycles by 90 percent, lowered GPU memory usage by 40 percent, and sustained high throughput inference across distributed workloads. Proficient in Python, PyTorch, LangChain, LangGraph, FastAPI, Docker, and continuous integration and delivery.

\section{Technical Skills}
\begin{itemize}[leftmargin=*,itemsep=2pt]
\item \textbf{Programming Languages:} Python, C++, C, Java, C Sharp, Go, Bash, SQL
\item \textbf{Large Language Models:} LLM fine-tuning, LoRA, PEFT, QLoRA, prompt engineering, agent orchestration, function calling, token optimization, guardrails, model evaluation
\item \textbf{LLM Frameworks:} LangChain, LangGraph, LlamaIndex, Hugging Face Transformers, Diffusers, LiteLLM, OpenAI, Anthropic, Google Gemini
\item \textbf{Generative AI:} Stable Diffusion, SDXL, Playground v2.5, Real-ESRGAN, SwinIR, CLIP, DINOv2, SAM, faster-whisper, retrieval augmented generation
\item \textbf{Machine Learning and Deep Learning:} PyTorch, TensorFlow, scikit-learn, convolutional neural networks, transformers, computer vision, natural language processing
\item \textbf{Vector Databases and Retrieval:} FAISS, Qdrant, Chroma, Pinecone, hybrid retrieval, re-ranking, embeddings
\item \textbf{MLOps and LLMOps:} model deployment, inference optimization, model versioning, experiment tracking, A/B testing, continuous integration and delivery
\item \textbf{Observability and Optimization:} structured logging, metrics, distributed tracing, GPU optimization, xFormers, ONNX, TensorRT, quantization, distributed training
\item \textbf{Cloud Platforms:} AWS, EC2, S3, IAM, GPU instances g5.4xlarge and g5.8xlarge, Azure virtual machines, Azure Container Apps, Azure Blob Storage, SaladCloud
\item \textbf{Infrastructure and DevOps:} Docker, Kubernetes, Helm, systemd, GitHub Actions, continuous integration and delivery pipelines
\item \textbf{Backend and System Design:} FastAPI, WebSocket, REST API design, asynchronous API, microservices architecture, distributed systems, scalable systems
\item \textbf{Backend Services:} Redis, Celery, RQ, message queues, caching, load balancing, rate limiting
\item \textbf{Data Engineering:} Pandas, NumPy, ETL pipelines, data pipelines, data validation, web scraping, Apify, Selenium, BeautifulSoup
\item \textbf{Security and Reliability:} sandboxed execution, AST validation, input sanitization, secrets management, high availability, fault tolerance
\item \textbf{Developer Tools:} Git, GitHub Actions, Linux, Ubuntu, Bash scripting, unit testing, integration testing
\end{itemize}

\section{Professional Experience}

\textbf{AI and DevOps Engineer} \hfill Nov 2025 -- Present\\
\textit{Zedny INC, Cairo, Egypt (On-site)}
\begin{itemize}
\item Architected production-grade AI platforms on microservices, delivering scalable large language model inference services across distributed GPU clusters serving over 10,000 daily requests with 99.9 percent uptime.
\item Designed end-to-end MLOps and LLMOps pipelines covering data ingestion, training, evaluation, serving, and model versioning, reducing deployment cycle time by 60 percent.
\item Orchestrated GPU workloads with Docker and Kubernetes through autoscaling and resource quotas, increasing throughput by 45 percent while cutting cloud costs by 30 percent.
\item Built continuous integration and delivery pipelines with GitHub Actions for automated testing, container builds, and zero-downtime deployments, shipping over 50 releases per month.
\item Implemented observability stacks with structured logging, metrics, and distributed tracing, reducing mean time to detect production issues by 70 percent.
\item Optimized inference cost and latency through request batching, caching, and model quantization, lowering p95 latency by 35 percent and cloud spend by 25 percent.
\item Defined API contracts, system boundaries, and service level objectives with product teams, translating AI requirements into scalable production services.
\item Hardened multi-tenant AI deployments with secrets management, rate limiting, and failover strategies.
\end{itemize}

\textbf{AI and Machine Learning Engineer} \hfill Sep 2024 -- Oct 2025\\
\textit{VEEM Solutions (Shrwd.ai Platform), Jeddah, Saudi Arabia (Remote)}
\begin{itemize}
\item Developed a large-scale multi-agent large language model system with dynamic tool orchestration and a retrieval augmented generation knowledge layer, enabling autonomous task execution across more than five business domains.
\item Engineered multilingual retrieval pipelines using FAISS vector search, MiniLM embeddings, hybrid retrieval, and re-ranking, improving answer relevance by 40 percent and reducing hallucinations by 50 percent.
\item Applied prompt engineering, model evaluation, and guardrails with schema validation to stabilize agent behavior across production traffic handling over 1,000 daily conversations.
\item Architected the Shrwd.ai brand intelligence platform integrating large-scale web crawlers, SEO analytics, and interactive dashboards for real-time tracking of more than 100 brands.
\item Created real-time FastAPI and WebSocket services with Redis caching and Celery workers, sustaining over 500 concurrent large language model inference sessions under production load.
\item Deployed services on Azure virtual machines and Container Apps with Docker and continuous integration and delivery, achieving zero-downtime releases across staging and production.
\item Instrumented pipelines with logging, metrics, and alerting to track retrieval quality, token usage, and latency, enabling data-driven iteration on prompts and models.
\end{itemize}

\textbf{AI Engineer (Part-time)} \hfill Nov 2024 -- Dec 2025\\
\textit{DigiTee.io, Cayman Islands (Remote)}
\begin{itemize}
\item Led development of NFT Wear AI, fine-tuning Stable Diffusion with LoRA to auto-generate apparel mockups, compressing design cycles from over four hours to under five minutes, a 95 percent reduction.
\item Created generative pipelines for the Mintora platform using Playground v2.5 and SDXL, integrating conversational user experience, rembg background removal, and Real-ESRGAN and SwinIR upscaling.
\item Architected and shipped Audira, a multi-agent voice platform with memory, faster-whisper speech to text, text to speech, and tool orchestration, enabling real-time multilingual onboarding.
\item Deployed and scaled GPU inference on AWS g5.4xlarge and g5.8xlarge instances with queue-based job distribution and load balancing, sustaining over 200 concurrent inference requests.
\item Reduced GPU out-of-memory incidents by 80 percent and improved throughput by 40 percent through xFormers, gradient checkpointing, memory efficient attention, and mixed precision inference.
\item Owned deployment, monitoring, and incident response across environments, including log aggregation and GPU utilization tracking for production inference workloads.
\end{itemize}

\textbf{Freelance AI and Machine Learning Engineer} \hfill 2024 -- 2026\\
\textit{Independent Consulting, Remote}
\begin{itemize}
\item Delivered over ten retrieval augmented generation systems for international clients, integrating FAISS, Hugging Face embeddings, FastAPI, and WebSocket APIs for contextual question answering at scale.
\item Engineered custom multi-agent architectures with LangChain and LangGraph, automating complex business workflows through external tool and API integration.
\item Created real-time voice assistants combining faster-whisper speech to text and multilingual text to speech pipelines, achieving sub-second response latency.
\item Deployed AI services across Azure, AWS, and SaladCloud, owning model selection, fine-tuning, infrastructure provisioning, and post-deployment monitoring.
\item Advised clients on architecture tradeoffs, cost optimization, and evaluation strategies, translating ambiguous requirements into production-ready AI solutions.
\end{itemize}

\textbf{AI Instructor} \hfill Oct 2024 -- Apr 2025\\
\textit{USAID, Ahmed Diefalla International Applied Technology School, Cairo, Egypt}
\begin{itemize}
\item Delivered structured curricula in software engineering, Python, AI, and robotics to over 100 students through project-based learning.
\item Guided end-to-end capstone projects covering problem framing, implementation, and deployment, strengthening technical and analytical skills.
\end{itemize}

\textbf{Programming Content Creator (Part-time)} \hfill Mar 2024 -- Mar 2025\\
\textit{Tweet Kod, Karabuk, Turkey (Remote)}
\begin{itemize}
\item Authored Python programming curricula for youth learners, producing over 50 hands-on projects and assessment modules.
\item Mentored students through graduation projects, improving coding proficiency and engineering reasoning.
\end{itemize}

\textbf{Programming and AI Instructor (Part-time)} \hfill Jan 2024 -- Dec 2024\\
\textit{Future Kids, Codemy, Code and Barmja, Cairo, Egypt (Remote)}
\begin{itemize}
\item Taught Scratch, Python, Java, HTML, AI fundamentals, and Pygame across diverse age groups.
\item Designed tailored lesson plans fostering creativity, critical thinking, and programming confidence for over 200 learners.
\end{itemize}

\section{Selected Projects}

\textbf{DataOps LLM Engine} \hfill \href{https://github.com/Islam-hady9/dataops-llm-engine}{GitHub Link}
\begin{itemize}
\item Built a large language model powered data operations engine enabling natural language interaction with Excel, CSV, and pandas DataFrames by translating user intent into safe executable Python code.
\item Engineered a multi-provider abstraction layer via LiteLLM supporting OpenAI, Anthropic, and Google Gemini with unified prompting, failover, and cost-aware routing, reducing provider lock-in risk.
\item Designed a seven-layer security architecture featuring AST validation, import whitelisting, sandboxed execution, resource limits, timeout enforcement, output sanitization, and audit logging.
\item Delivered a FastAPI REST interface with asynchronous execution and schema validation, supporting over 100 requests per second with structured JSON responses.
\item Optimized for developer usability and scalability, exposing a clean software development kit and high throughput API with separation between reasoning, validation, and execution layers.
\end{itemize}

\textbf{Eyes Mate: AI Assistant for the Visually Impaired} \hfill \href{https://github.com/Islam-hady9/application-to-help-the-blind-eyes-mate}{GitHub Link}
\begin{itemize}
\item Developed a production-style assistive AI system combining object recognition, distance estimation, optical character recognition, currency recognition, and face recognition with real-time voice feedback.
\item Integrated speech and computer vision pipelines into a unified low-latency experience, achieving response times under two seconds on mobile hardware.
\end{itemize}

\textbf{Brain Tumor Detection API} \hfill \href{https://github.com/Islam-hady9/BrainTumorDetection-API}{GitHub Link}
\begin{itemize}
\item Built a convolutional neural network pipeline for brain tumor classification from MRI scans, reaching over 95 percent validation accuracy, packaged as a production-ready REST API with versioned endpoints.
\item Designed structured request and response schemas with error handling for safe integration into downstream medical applications.
\end{itemize}

\textbf{Generative AI Models} \hfill \href{https://github.com/Islam-hady9/Generative-AI-Models}{GitHub Link}
\begin{itemize}
\item Implemented and benchmarked transformer and diffusion-based architectures for text-to-image and image-to-text tasks across multiple datasets.
\item Explored fine-tuning, evaluation, and prompt strategies for creative and practical generative AI applications.
\end{itemize}

\textbf{SmartAI Customer Support} \hfill \href{https://github.com/Islam-hady9/SmartAI_CustomerSupport}{GitHub Link}
\begin{itemize}
\item Designed a retrieval augmented generation powered customer support assistant with multilingual grounding, improving answer accuracy by 45 percent over baseline large language model responses.
\item Integrated retrieval, re-ranking, and generation into a unified inference service with structured logging and evaluation hooks.
\end{itemize}

\textbf{Deep CUDA: GPU Acceleration from Scratch} \hfill \href{https://github.com/Islam-hady9/deep-cuda}{GitHub Link}
\begin{itemize}
\item Implemented a full convolutional neural network in raw CUDA C++ for MNIST classification with custom kernels for convolution, matrix multiplication, and backpropagation without high-level frameworks.
\item Optimized GPU performance through shared memory, thread and block scheduling, and parallel reduction, achieving a tenfold speedup over the CPU baseline.
\end{itemize}

\section{Education}

\textbf{Master of Science in Data Science (Preparatory Year)} \hfill 2026 -- Present\\
\textit{Faculty of Computers and Artificial Intelligence, Helwan University, Cairo, Egypt}\\
Focus areas: machine learning, statistical analysis, applied data science.

\textbf{Bachelor of Science in Computer Science} \hfill 2020 -- 2024\\
\textit{Faculty of Computers and Information, Assiut University, Assiut, Egypt}\\
Relevant coursework: machine learning, deep learning, computer vision, parallel computing.

\section{Certifications}
\begin{itemize}
\item \textbf{LLMOps and AIOps Bootcamp with Eight End-to-End Projects}, Udemy, KRISHAI Technologies \hfill Mar 2026\\
\href{https://drive.google.com/file/d/1LRMq4abpNwBmxEh_bcviQSFq132oCCFC/view?usp=drive_link}{Certificate Link}
\item \textbf{Generative AI with Large Language Models}, Coursera \hfill Apr 2025\\
\href{https://drive.google.com/file/d/1qkDcCiYGasivGr5Ozfq51DuBgaE9j0fO/view?usp=drivesdk}{Certificate Link}
\item \textbf{Advanced Learning Algorithms}, DeepLearning.AI \hfill Sep 2023\\
\href{https://drive.google.com/file/d/1Z9-hwfvvIeLOC-8foyEUdOdJaSkE454v/view}{Certificate Link}
\item \textbf{Deep Learning with PyTorch: Image Segmentation}, Coursera \hfill Sep 2023\\
\href{https://drive.google.com/file/d/1byehbMkf4Dr-BL1l5z1EIZo6ju8OVS-5/view}{Certificate Link}
\item \textbf{Empedia Competitive Programming Competition}, Empedia \hfill Aug 2023\\
\href{https://drive.google.com/file/d/1N9leyAlDCAoQzjANXn2pMyp6Ec1NC_Td/view}{Certificate Link}
\item \textbf{Mathematics for Computer Science}, BIO CODE, Assiut University \hfill Aug 2023\\
\href{https://drive.google.com/file/d/1XvkvbVA_PuUV7hGh3bC6Cu3Z-ZVlwk1D/view}{Certificate Link}
\item \textbf{Supervised Machine Learning: Regression and Classification}, DeepLearning.AI \hfill Mar 2023\\
\href{https://drive.google.com/file/d/1FOQtu1kBrybHJn99R28ZX3afhqk_I6Wj/view}{Certificate Link}
\item \textbf{Python Programming Basics}, MaharaTech \hfill Feb 2023\\
\href{https://drive.google.com/file/d/13DwIJIlSSwFtjmZxjMQ2dic9SpJJu5SY/view}{Certificate Link}
\item \textbf{Database Fundamentals}, MaharaTech \hfill Feb 2023\\
\href{https://drive.google.com/file/d/1YMmTIxpXn5Nbpqqwb5jBVqCpGkQrXioX/view}{Certificate Link}
\end{itemize}

\section{Publications and Research}
\begin{itemize}
\item \textbf{AI Traffic Violation in Smart Cities and Flying Vehicles.} Research on AI-driven real-time monitoring, detection, and enforcement systems for intelligent transportation and urban mobility.
\end{itemize}

\section{Languages}
Arabic (Native) $|$ English (Professional)

\end{document}